%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Pranav Ponugoti} \\ \vspace{1pt}
%    123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 408-717-3909 ~ \href{mailto:pranav03@vt.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{pranav03@vt.edu}} ~ 
    \href{https://linkedin.com/in/pranav-ponugoti/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/pranav-ponugoti}}  ~
    \href{https://github.com/ponugotipranav}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/ponugotipranav}}
    % \vspace{-8pt}
    \vspace{-2pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virginia Polytechnic Institute and State University}{August 2021 -- December 2024}
      {Bachelor of Science in Computer Science, Minor in Mathematics \normalfont $|$ GPA: 3.36}{Blacksburg, VA}\\
      \vspace{9pt}
      {\small Relevant Coursework: Software Design \& Data Structures, Programming in Python, App Development with Docker, Computer Organization I, Computer Organization II, Data Structures \& Algorithms, Computer Systems, Data \& Algorithm Analysis, Artificial Intelligence, Multivariable Calculus, Discrete Math, Linear Algebra, Applied Combinatorics, Statistics}
      \vspace{-3pt}
    \resumeSubheading
      {Homestead High School}{August 2017 -- June 2021}
      {High School Diploma}{Cupertino, CA}\\
  \resumeSubHeadingListEnd
% \vspace{-4pt}
% \small \textbf{Relevant Coursework:} Data Structures \& Algorithms, Programming in Python, App Development with Docker, Computer Organization, Computer Systems, Artificial Intelligence, Data \& Algorithm Analysis, Multivariable Calculus, Discrete Math, Statistics
\vspace{-10pt}


% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Virginia Tech College of Engineering}{August 2023 -- December 2023}
      {Undergraduate Research $|$ Field Study}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Collaborated closely with fellow researchers to improve the design and functionality of TERRY, a trash-collecting robot.}
        \resumeItem{Utilized Arduino to integrate video streaming capabilities, while applying PyTorch and OpenCV to implement sophisticated computer vision functionality.}
        \resumeItem{Assisted in troubleshooting technical issues and debugging code to ensure optimal performance of robot in field trials.}
        \resumeItem{Presented research findings and project updates to stakeholders, including faculty advisors and industry partners.}
    \resumeItemListEnd

    \resumeSubheading
      {Digital Cues, Inc.}{April 2023 -- August 2023}
      {Software Engineering Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Developed and documented automation workflows, optimizing processes across various applications and services.}
        \resumeItem{Leveraged Postman to conduct thorough testing and validation of APIs, ensuring reliability and functionality across different endpoints and environments. Explored use of several RESTful APIs, such as Microsoft's Office 365 APIs.}
        \resumeItem{Assisted in designing and implementing robust, scalable, and maintainable code solutions to meet project requirements.}
    \resumeItemListEnd

    \resumeSubheading
      {Homestead High School}{August 2020 -- June 2021}
      {Student Tutor}{Cupertino, CA}
      \resumeItemListStart
        \resumeItem{Collaborated with instructor to draft coursework, with a focus on maximizing student comprehension and retention.}
        \resumeItem{Worked one on one with over 30 students to foster an enriched learning atmosphere and hone their mathematical skills.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
% \vspace{-16pt}
\vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Portfolio Website} $|$ \emph{JavaScript, HTML/CSS, React, Git, Docker}}{}
          \resumeItemListStart
            \resumeItem{Developed a professional portfolio website, utilizing a streamlined template, to showcase skills, projects, and more.}
            \resumeItem{Deployed website on GitHub Pages for easy access and visibility. Available at \href{https://ponugotipranav.github.io}{https://ponugotipranav.github.io}}
          \resumeItemListEnd
          \vspace{-15pt}
      \resumeProjectHeading
          {\textbf{SimpleWPM} $|$ \emph{JavaScript, HTML/CSS, Git}}{}
          \resumeItemListStart
            \resumeItem{Created a minimalistic browser-based tool to evaluate user typing speed: \href{https://ponugotipranav.github.io/SimpleWPM}{https://ponugotipranav.github.io/SimpleWPM}}
          \resumeItemListEnd
          \vspace{-15pt}
      \resumeProjectHeading
          {\textbf{Berkeley AI Pac-Man Projects} $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Completed series of AI projects from UC Berkeley, covering topics such as search algorithms and reinforcement learning.}
          \resumeItemListEnd
          \vspace{-15pt}
      \resumeProjectHeading
          {\textbf{Customizable Shell} $|$ \emph{C, Python, Git}}{}
          \resumeItemListStart
            \resumeItem{Engineered a custom shell with several built-in commands and advanced features including pipelines and IO redirection.}
            \resumeItem{Implemented resilient error handling mechanisms and optimized memory management for efficient command execution.}
            \resumeItem{Developed comprehensive test scripts in Python to validate shell functionality and ensure ideal performance.}
          \resumeItemListEnd
          \vspace{-15pt}
      \resumeProjectHeading
          {\textbf{Data Sorter} $|$ \emph{Java, JUnit}}{}
          \resumeItemListStart
            \resumeItem{Implemented a modified Quicksort algorithm to sort binary and ASCII files, concurrently generating runtime statistics.}
            \resumeItem{Designed a custom buffer pool with LRU replacement for efficient byte array management and disk I/O operations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
% \vspace{-15pt}
\vspace{-12pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages:}{ Python, Java, C, JavaScript, HTML/CSS, SQL, MATLAB} \\
     % \textbf{Developer Tools:}{ Postman, Docker, VS Code, Eclipse} \\
     \textbf{Technologies/Frameworks:}{ Node.js, React, Git, Linux, NumPy, Pandas, PyTorch, OpenCV, MongoDB, Postman, Docker} \\
     \textbf{Achievements:}{ Dean's List Recipient, AP Scholar Award} \\
    }}
 \end{itemize}
 \vspace{-16pt}


% %-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%             \resumeItemListStart
%                 \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%                 \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%                 \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd


\end{document}